\Large\textbf{Preparation GUIDE for Initial-Submission Manuscript}\\~\\ \large\textbf{ Preparation of Papers in Two-Column Format\\ for the ASP-DAC 2014 (\LaTeX2e version)}

### 2013-11-21 exps.tex
changing exp

\begin{table}[t]
\twocolumn[
\centering
\begin{@twocolumnfalse}
\caption{Benchmark programs using \texttt{delay} constructs} \label{fig:comparison}
\resizebox{18cm}{2.4cm}{
\begin{tabular}{| c | c | c | c | c | c | c |}
	\cline{3-7}
	\multicolumn{2}{c|}{}											& HRTCS 		& Motor 		  & Robot 			  & AECS/CD1  		   & AECS/CD2\\ \hline
								 \multicolumn{2}{|c|}{BCRT} 		&0.0334 ms 		& 0.0361 ms		  & 0.0325 ms		  & 0.1683 ms		   & 0.1881 ms\\ \cline{1-7}
								 \multicolumn{2}{|c|}{WCRT} 		&0.1120 ms 		& 0.1116 ms		  & 0.0601 ms		  & 0.7147 ms		   & 1.0115 ms\\ \cline{1-7}
								 \multirow{2}{*}{Delay 1}	 & M..N &50.3-200.3 ms 	& 2.4-7.4772 ms	  & 1230-2274.0263 ms & 10000-42473.2197 ms& 10000-53772.0045 ms \\ \cline{2-7}
											   & d			 		&1506-1787  	& 67 			  & 37861			  & 59427		       &53160\\ \cline{1-7}
								 \multirow{2}{*}{Delay 2}	 & M..N & 	N/A 		& 1.667-5.2452 ms & N/A				  & N/A 			   &10000-53772.0045 ms\\ \cline{2-7}
											   & d			 		& 	N/A	 		& 47			  & N/A				  & N/A       		   &53160\\ \cline{1-7}
								 \multirow{2}{*}{Delay 3}	 & M..N & 	N/A	 		& 0.05-0.2232 ms  & N/A				  & N/A       		   &N/A\\ \cline{2-7}
											   & d			 		& 	N/A	 		& 2		      	  &	N/A				  & N/A       		   &N/A\\ \cline{1-7}
								 \multirow{2}{*}{Delay 4}	 & M..N & 	N/A	 		& 0.3-1.0044 ms   & N/A				  &	N/A       		   &N/A\\ \cline{2-7}
											   & d				 	& 	N/A	 		& 9				  & N/A				  &	N/A      		   &N/A\\ \cline{1-7}
								 \multirow{2}{*}{Delay 5}	 & M..N & 	N/A	 		& 0.733-2.3436 ms & N/A				  &	N/A      		   &N/A\\ \cline{2-7}
											   & d			 		& 	N/A	 		& 21 			  &	N/A				  & N/A      		   &N/A\\ \hline
% 	\multirow{12}{*}{TP-JOP} 	& \multicolumn{2}{|c|}{BCRT} 		&0.0028 ms 		& 0.0060 ms		  & 0.0011 ms		  & 0.0532 ms		   & 0.0292 ms\\ \cline{2-8}
% 								& \multicolumn{2}{|c|}{WCRT} 		&0.0329 ms 		& 0.0393 ms		  & 0.0361 ms		  & 0.5072 ms		   & 0.8388 ms\\ \cline{2-8}
% 								& \multirow{2}{*}{Delay 1}	 & M..N &50.3-600.3 ms 	& 2.4-15.6265 ms  & 1230-42317.8276 ms& 10000-95358.8578 ms& 10000-287757.9834 ms \\ \cline{3-8}
% 								&			   & d			 		&18209-18232 	& 398 			  & 1171429			  & 188015		       &343054\\ \cline{2-8}
% 								& \multirow{2}{*}{Delay 2}	 & M..N & 	N/A 		& 1.667-10.8757 ms& N/A				  & N/A 			   &10000-287757.9834 ms\\ \cline{3-8}
% 								&			   & d			 		& 	N/A	 		& 277			  & N/A				  & N/A       		   &343054\\ \cline{2-8}
% 								& \multirow{2}{*}{Delay 3}	 & M..N & 	N/A	 		& 0.05-0.3534 ms  & N/A				  & N/A       		   &N/A\\ \cline{3-8}
% 								&			   & d			 		& 	N/A	 		& 9		      	  &	N/A				  & N/A       		   &N/A\\ \cline{2-8}
% 								& \multirow{2}{*}{Delay 4}	 & M..N & 	N/A	 		& 0.3-1.9631 ms   & N/A				  &	N/A       		   &N/A\\ \cline{3-8}
% 								&			   & d				 	& 	N/A	 		& 50			  & N/A				  &	N/A      		   &N/A\\ \cline{2-8}
% 								& \multirow{2}{*}{Delay 5}	 & M..N & 	N/A	 		& 0.733-4.79 ms   & N/A				  &	N/A      		   &N/A\\ \cline{3-8}
% 								&			   & d			 		& 	N/A	 		& 122 			  &	N/A				  & N/A      		   &N/A\\ \cline{2-8}
% 	\hline
\end{tabular}
}
\end{@twocolumnfalse}
]
\end{table}

% \begin{figure}
% \centering
% 	\includegraphics[trim=2cm 2cm 2cm 2cm,scale=0.5]{table2}
%         \caption{Evaluation of logical delays \emph{d} for on various
%           benchmark programs}\label{fig:comparison}
% \end{figure}

We have carried out a number of experiments on a set of applications
with real-time constraints. The benchmark set is shown in
Table~\ref{fig:comparison}. HRCTS is the human response system described
in Figure~\ref{fig:1}. AECS (Access and Environmental Control System) is
an application that controls an intelligent room environment described
in~\cite{aecs_ispa}. The system interacts with two external timers
through input/output signals in order to measure how long the entrance
door to the room is being opened and time the illegal presence (e.g.
intruder) that is being detected. The program has been modified such
that the delay constructs are used instead of external timers as shown
in~\ref{delaycode}.

\begin{figure}[h!]
	\begin{SubFloat}{\label{delaycode:a}sss}
		\centering
		\begin{minipage}[b]{0.3\linewidth}
			\footnotesize
\begin{verbatim}
emit TimerTriggered;
trap(T){
  abort(DoorOpened){
    await(TimeOut);
    exit(T); 
  }
}
\end{verbatim}
		\end{minipage}
	\end{SubFloat}
\hspace{1cm}%
	\begin{SubFloat}{\label{delaycode:b}sss}
		\centering
		\begin{minipage}[b]{0.3\linewidth}
			\footnotesize
\begin{verbatim}
// No emit statement
trap(T){
  abort(DoorOpened){
    delay(2.4 .. 7.4772 ms);
    exit(T);  
  }
}
\end{verbatim}
		\end{minipage}
	\end{SubFloat}
\caption{www}
\label{delaycode}
\end{figure}

Motor is a stepper motor controller from~\cite{Bourke2009a}. Robot is an
industrial automation application that consists of two manufacturing
belts and a robotic arm that splits goods according to their volumes.
HRCTS consists of 2 CDs, but only one with real-time delays. AECS also
has 2 CDs; CD1 consist of a single delay statement, while CD2 has 2
delay statements. Robot and Motor both are synchronous programs with 1
and 5 delay statements, respectively. All these examples are written in
the SystemJ language. The requirement to have deterministic or
non-deterministic delays varies between each benchmark. These delay
requirements are shown in Table~\ref{fig:comparison} (\texttt{M..N}).

@@

We use the \textit{Java Optimized Processor}
(JOP)~\cite{jop:jnl:jsa2007}, to carry out all our experiments. JOP
implements the JVM specification in hardware directly, and has been
shown to be real-time amenable. We statically estimate the WCRT and BCRT
of these benchmark applications using the real-time analysis tools
provided by the JOP design framework. The \textit{Safety Critical Java}
(SCJ) specification we use for real-time analysis avoids garbage
collection (GC) and hence, GC overheads and unpredictability are
completely avoided.

@@

% The upper bound \texttt{N} needed to be relaxed for all examples other
% than HRCTS to obtain a feasible \texttt{d}. Therefore,
Algorithm \ref{alg:2} is applied to those examples, where relaxation was
required, to determine the minimum upper real-time bound \emph{N} such
that there exist a solution for \emph{D} in Algorithm \ref{alg:1}. This
algorithm gives a unique number for logical tick delay \emph{d} such
that \emph{d} = Min(\emph{$S_2$}) = Max(\emph{$S_1$}).  The compiler,
therefore, will choose \emph{d} based on the newly computed \emph{N} for
the examples: Robot, Motor and AECS.

>>>>

{\renewcommand{\arraystretch}{0.9}
\begin{table}[t]
	\small
	\centering
	\caption{Program specification}
	\label{fig:benchlist}
	\scalebox{0.9}{
\begin{tabular}{cccc}
\toprule
\emph{Benchmark}       & \emph{Required delays} & \emph{\# of CDs} & 
\emph{Lines of code}        
\\ \midrule
HRTCS                  & 50.3-200.3 ms & 2                  & 56
\\ \midrule
\multirow{5}{*}{Motor} & 2.4 ms        & \multirow{5}{*}{1} & \multirow{5}{*}{116} \\ 
                       & 1.667 ms      &                    &                      \\ 
                       & 0.05 ms       &                    &                      \\ 
                       & 0.3 ms        &                    &                      \\ 
											 & 0.733 ms      &                    &
\\ \midrule
Printer                & TBC           & 2                  & 39
\\ \midrule
AECS/CD1               & 10000 ms      & -                  & 144
\\ \midrule
AECS/CD2               & 10000 ms      & -                  & 123
\\ \bottomrule
\end{tabular}
}
\vspace{-20pt}
\end{table}
}

{\renewcommand{\arraystretch}{0.6}
\begin{table}[t]
\twocolumn[
\centering
\begin{@twocolumnfalse}
	\caption{Actual delays obtained for \texttt{delay} constructs in the
benchmark programs based on their BCRT and WCRT}
\label{fig:comparison}
\begin{tabular}{ c  c  c  c  c  c  c }
	\toprule
	\multicolumn{2}{c}{}											& \emph{HRTCS} 		&
	\emph{Motor} 		  & \emph{Robot} 			  & \emph{AECS/CD1}   &
	\emph{AECS/CD2} \\ \midrule
	\multicolumn{2}{c}{\emph{BCRT}} 		&0.0334 ms 		& 0.0361 ms		  &
	0.0325 ms		  & 0.1683 ms		   & 0.1881 ms\\ \cmidrule(r){1-7}
	\multicolumn{2}{c}{\emph{WCRT}} 		&0.1120 ms 		& 0.1116 ms		  &
	0.0601 ms		  & 0.7147 ms		   & 1.0115 ms\\ \cmidrule(r){1-7}
								 \multirow{2}{*}{Delay 1}	 & M..N &50.3-200.3 ms 	& 2.4-7.4772 ms	  & 1230-2274.0263 ms & 10000-42473.2197 ms& 10000-53772.0045 ms \\ \cmidrule(r){2-7}
											   & d			 		&1506-1787  	& 67 			  & 37861			  & 59427		       &53160\\ \cmidrule(r){1-7}
								 \multirow{2}{*}{Delay 2}	 & M..N & 	N/A 		& 1.667-5.2452 ms & N/A				  & N/A 			   &10000-53772.0045 ms\\ \cmidrule(r){2-7}
											   & d			 		& 	N/A	 		& 47			  & N/A				  & N/A       		   &53160\\ \cmidrule(r){1-7}
								 \multirow{2}{*}{Delay 3}	 & M..N & 	N/A	 		& 0.05-0.2232 ms  & N/A				  & N/A       		   &N/A\\ \cmidrule(r){2-7}
											   & d			 		& 	N/A	 		& 2		      	  &	N/A				  & N/A       		   &N/A\\ \cmidrule(r){1-7}
								 \multirow{2}{*}{Delay 4}	 & M..N & 	N/A	 		& 0.3-1.0044 ms   & N/A				  &	N/A       		   &N/A\\ \cmidrule(r){2-7}
											   & d				 	& 	N/A	 		& 9				  & N/A				  &	N/A      		   &N/A\\ \cmidrule(r){1-7}
								 \multirow{2}{*}{Delay 5}	 & M..N & 	N/A	 		& 0.733-2.3436 ms & N/A				  &	N/A      		   &N/A\\ \cmidrule(r){2-7}
											   & d			 		& 	N/A	 		& 21 			  &	N/A
												 & N/A      		   &N/A\\ \bottomrule
\end{tabular}
\end{@twocolumnfalse}
]
\end{table}
}

We have carried out a number of experiments on a set of applications
with real-time constraints. The characteristics of the benchmark set
including delay specifications are shown in Table~\ref{fig:benchlist}.

HRTCS is the human response system described in
Section~\ref{sec:motivating-example}. AECS (Access and Environmental
Control System) is an application that controls an intelligent room
environment described in~\cite{aecs_ispa}.  The system interacts with
two external timers through input/output signals in order to measure how
long the entrance door to the room is being opened and time the illegal
presence (e.g. intruder) that is being detected. The program has been
modified such that the delay constructs are used instead of external
timers as shown in Figure~\ref{delaycode}. In the original AECS, the
system needed to trigger external timer by emitting the output signal in
order to wait for a specific amount of time (e.g.
\texttt{TimerTriggered} in Figure~\ref{delaycode:a}). When the timer
expires, it notifies back to the system through the input signal
\texttt{TimeOut} which is polled at the \texttt{await} statement. With
the new delay constructs, those timers are not necessary and delays can
be expressed directly in the code as shown in Figure~\ref{delaycode:b}.
\begin{figure}[h!]
	\begin{SubFloat}{\label{delaycode:a}}
		\centering
		\begin{minipage}[b]{0.3\linewidth}
			\scriptsize
\begin{verbatim}
emit TimerTriggered;
trap(T){
  abort(DoorOpened){
    await(TimeOut);
    exit(T); 
  }
}
\end{verbatim}
		\end{minipage}
	\end{SubFloat}
\hspace{1cm}%
	\begin{SubFloat}{\label{delaycode:b}}
		\centering
		\begin{minipage}[b]{0.5\linewidth}
			\scriptsize
\begin{verbatim}
// No emit statement
trap(T){
  abort(DoorOpened){
    delay(2.4 ms);
    exit(T);  
  }
}
\end{verbatim}
		\end{minipage}
	\end{SubFloat}
\caption{Replacing external timer with delay construct}
\label{delaycode}
\end{figure}
Motor is a stepper motor controller from~\cite{Bourke2009a}, used for
producing monochrome images on paper by applying a correct application
of current to the print head (a row of resistors). In this example,
duration of current applied to the print head is controlled based on
feedback logic where delays are expressed in real-time Esterel
constructs. We have rewritten the program in SystemJ with our delay
construct and compare between desired and relaxed delay according to
WCRT and BCRT of the program. Printer is an example from [], which
models a printer and a spooler in timed CSP. Their operation is rather
simple: as soon as the spooler receives a print job, passes it to the
printer through channel for processing. The example demonstrates that by
specifying delay bounds (e.g. 1 to 5 time units) between two subsequent
behaviors, the job is passed along the channel as soon as both processes
become ready.

%Robot is an industrial automation application that consists of two
%manufacturing belts and a robotic arm that splits goods according to
%their volumes.

HRTCS consists of 2 CDs, but only one with real-time delays. AECS also
has 2 CDs; CD1 consist of a single delay statement, while CD2 has 2
delay statements. In this case, as explained previously, delay
statements replaced the external timers and corresponding interface
signals. The system triggers an alarm after 10 seconds of detection of
an intruder or generates a beep sound when an entrance door is being
opened for the same amount of time. For Printer, each spooler and
printer process is mapped to a single clock-domain. Spooler CD sends a
job to the Printer CD between [] to [] ms after receiving it from the
enviornment (e.g. a user). On the other hand, Printer CD notifies
environment that it starts printing between [] to [] ms once it receives
the job from the Spooler CD. Actual print job is started between [] to
[] after the notification. Lastly, Motor is a synchronous program with 5
delay statements where they controls amount of current into the stepper
motor coils.

%All these examples are written in
%the SystemJ language. The requirement to have deterministic or
%non-deterministic delays varies between each benchmark.  These delay
%requirements are shown in Table~\ref{fig:comparison} (\texttt{M..N}).

@@

We use the \textit{Java Optimized Processor}
(JOP)~\cite{jop:jnl:jsa2007}, to carry out all our experiments. JOP
implements the JVM specification in hardware directly, and has been
shown to be real-time amenable. We statically estimate the WCRT and BCRT
of these benchmark applications using the real-time analysis tools
provided by the JOP design framework. The \textit{Safety Critical Java}
(SCJ) specification we use for real-time analysis avoids garbage
collection (GC) and hence, GC overheads and unpredictability are
completely avoided. Note that only HRTCS and Printer have
non-deterministic delays (\texttt{M..N}) as their program specification
where others use exact delays (\texttt{M}). The actual delay after
applying relaxation for the upper real-time bound is shown in
Table~\ref{fig:comparison}.

@@

% The upper bound \texttt{N} needed to be relaxed for all examples other
% than HRTCS to obtain a feasible \texttt{d}. Therefore,
Algorithm \ref{alg:2} is applied to those examples, where relaxation was
required, to determine the minimum upper real-time bound \emph{N} such
that there exist a solution for \emph{D} in Algorithm \ref{alg:1}. This
algorithm gives a unique number for logical tick delay \emph{d} such
that \emph{d} = Min(\emph{$S_2$}) = Max(\emph{$S_1$}).  The compiler,
therefore, will choose \emph{d} based on the newly computed \emph{N} for
the examples: Printer, Motor and AECS.
